---
title: Journal Club 2017
summary: 논문 발표 일정입니다.
---

```{r setup, include = FALSE}
source("function.R")
```

The materials shown here is low-resolution and only for the purpose of preview. 
High-resolution presentation files may be available upon request. Please use `Mail` button of the navigation bar.
If you have an access to the NAS server of AMC CPT, you can find it from `CPT documents/BookJournal` folder. (or click the <i class="fa fa-file-pdf-o"></i> icon - exclusively working in the NASAN or wired netword of AMC.)

```{r}
cptid <- "2017-01-06-gcpark-ebola"
DOI   <- "10.1177/2051013615611017"
Journal(cptid, DOI)
```

```{r}
cptid <- "2017-01-13-shan-neurodegen"
DOI   <- "10.1002/psp4.12155"
Journal(cptid, DOI)
```

```{r}
cptid <- "2017-02-10-gcpark-norendoxifen"
DOI <- "10.1021/jm501218e"
Journal(cptid, DOI)
```

```{r}
cptid <- "2017-02-24-shan-daclizumab"
DOI <- "10.1007/s40265-017-0708-2"
Journal(cptid, DOI)
```

```{r}
cptid <- "2017-03-17-yscho-Herceptin"
DOI <- "10.3389/fonc.2012.00062"
Journal(cptid, DOI)
```

```{r}
cptid <- "2017-03-17-gcpark-nanorods"
DOI <- "10.1002/adma.201605563"
Journal(cptid, DOI)
```

```{r}
cptid <- "2017-03-31-shan-pbpk"
DOI <- "10.1002/cpt.622"
Journal(cptid, DOI)
```

```{r}
cptid <- "2017-04-21-shan-rxode"
DOI <- "10.1002/psp4.12052"
Journal(cptid, DOI)
```

<!-- ```{r} -->
<!-- cptid <- "2017-04-07-yscho-genomeEdit" -->
<!-- DOI   <- "10.1002/cpt.542" -->
<!-- Journal(cptid, DOI) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- cptid <- "2017-04-07-skyoon-largepharma" -->
<!-- DOI   <- "10.1056/NEJMra1510069" -->
<!-- Journal(cptid, DOI) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- cptid <- "2017-04-14-gcpark-ngs"  -->
<!-- DOI <- "10.3389/fgene.2015.00215" # Clinical applications of next generation sequencing in cancer: from panels, to exomes, to genomes -->
<!-- Journal(cptid, DOI) -->
<!-- ``` -->

## Conversion

- Download `imagemagick` <http://www.imagemagick.org/script/download.php>
- Add the following script to the `~/.bashrc`

```bash
function pdfmontage(){
    rm $1*.png
    convert -density 300 $1.pdf -resize 600x480 $1_%03d.png
    montage -mode concatenate -tile 4x $1*.png $1-full.png
    convert $1-full.png -resize 25% $1.png
    rm $1_*.png
    cp $1.png ~/asancpt/asancpt.github.io/assets
}
```

- Run the lines in the bash terminal

```bash
pdfmontage filename-without-extension
```

- Git commit and push
